---
title: "Bootstrapping single cell data"
author: "Ruslan Strogantsev"
date: "9/27/2021"

output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
    fig_caption: yes
    fig_crop: no
    df_print: kable
    
editor_options:
  chunk_ouput_type: inline

---

```{r setup, include=FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
getwd()
```
```{r}
library(Seurat)
library(tidyverse)
library(sleepwalk)
library(patchwork)

theme_set(theme_bw(base_size = 10))
require(readr)
marrow.filt.integrated <- readr::read_rds("../Tet2_marrow_integrated_Dec20.rds")
getwd()


DefaultAssay(marrow.filt.integrated)<-"integrated"
DefaultAssay(marrow.filt.integrated)#check it's "integrated"

```

## Define Function to run bootsrap analysis on:

```{r}
run.bootstrap <- function(object, cluster, ident.1= "WT_unt", ident.2="KO_unt", n_reps=100, divider=4, cutoff=0.05){
  current_cells <- WhichCells(object, idents = cluster) #cluster is cluster of interest from the column of cluster names.  
  #Be sure to set the identity for this work: Idents(object) <- '{column name}'
  subset_current <- subset(object, cells = current_cells) #get an object of just that of the cluster
  marks <- NULL #list place holder
  count <- NULL #counter
  Idents(subset_current) <- "geno_treat" #change Idents according to comparison type to be made
  wt.cells <- WhichCells(object = subset_current, idents = ident.1)
  ko.cells <- WhichCells(object = subset_current, idents = ident.2)
  #wt.stm_cells <- WhichCells(object = subset_current, idents = "WT_IL1b")
  #ko.stm_cells <- WhichCells(object = subset_current, idents = "KO_IL1b")
  
  n_wt.cells <- length(wt.cells) # get lengths to get roughly even counts
  n_ko.cells <- length(ko.cells) # 
  #n_wt.stm_cells <- length(wt.stm_cells) #
  #n_ko.stm_cells <- length(ko.stm_cells) #
  
  min_cells <- ceiling(min(n_wt.cells,n_ko.cells)/divider) # get minimum cells, divider maybe set to 1 to have the same number as the minimum (thus the smaller set has no variability) or higher to decrease the number of cells and allow for more variability in the bootstrapping

  total_genes <- NULL #place holder for total genes
  #get a reference DE list to compare the bootstraps against
  all_markers <- FindMarkers(subset_current, ident.1 = ident.1, ident.2 = ident.2, assay = "RNA", logfc.threshold = 0.01, min.pct = 0)
  all_markers[["gene"]] <- rownames(all_markers)
  all_markers <- subset(all_markers, subset =  p_val_adj < 0.05)
  
  
  
  #bootstrap  define: n_reps
  for (i in 1:n_reps){
  item_name <- paste(cluster,i,sep="_")
  change_seed <- floor(runif(1)*100*i)
  set.seed(change_seed) #make things random
  wt_cell_sample <- sample(wt.cells, size = min_cells)
  mut_cell_sample <- sample(ko.cells, size = min_cells)
  seurat_sub_sample <- subset(subset_current, cells = c(wt_cell_sample,mut_cell_sample))
  total_genes <- c(total_genes,nrow(seurat_sub_sample))
  Idents(seurat_sub_sample) <- "geno_treat"
  marks[[as.character(i)]] <- FindMarkers(seurat_sub_sample, ident.1 = ident.1, ident.2 = ident.2, assay = "RNA", logfc.threshold = 0.01, min.pct = 0)
  marks[[as.character(i)]] <- marks[[as.character(i)]][which(marks[[as.character(i)]][,5] < cutoff),] # get adjusted p-val lower than cutoff
  colnames(marks[[as.character(i)]]) <- paste(colnames(marks[[as.character(i)]]),item_name,sep = "_")
    if (i > 1){
      #put them together in one list
      #marks[[as.character(i)]] <- marks[[as.character(i)]][,-c(3,4)]
      marks[[as.character(i)]] <- merge(marks[[as.character(i-1)]],marks[[as.character(i)]], by = 0, all = T)
      rownames(marks[[as.character(i)]]) <- marks[[as.character(i)]]$Row.names
      marks[[as.character(i)]] <- marks[[as.character(i)]][,-1] #remove Row.names
      count <- i
    }
    if (i == n_reps){
      #add a gene column
      marks[[as.character(i)]][["gene"]] <- rownames(marks[[as.character(i)]])
      marks[[as.character(i)]] <- gather(marks[[as.character(i)]], key = "avg_logFC", value = "avg_logFC_val", grep("log",colnames(marks[[as.character(i)]]), value = T))
    }
  }
  output<- list(all_markers, marks)
  return(output)
}
```


Now we can use the 'run.bootstrap' function passing on the following parameters:
object  Seurat_object
cluster Cell cluster of interest
ident.1 Comparator 1 default="WT_unt", 
ident.2 Comparator 2 default="KO_unt", 
n_reps  number of iterations to run, default=100, 
divider maybe set to 1 to have the same number as the minimum (thus the smaller set has no variability) or higher to decrease the number of cells and allow for more variability in the bootstrapping=2, 
cutoff  pvalue significance cut-off default=0.05

## save the R-object, all-gene markers and bootsrapping analysis output
```{r}

DefaultAssay(marrow.filt.integrated) <-'RNA'

Idents(marrow.filt.integrated) <- 'seurat_clusters'

marrow.filt.integrated <- RenameIdents(marrow.filt.integrated, `0` = "all", `1` = "all", `2` = "all", `3` = "all", `4` = "all", `5` = "all", `6` = "all", `7` = "all", `8` = "all", `9` = "all", `10` = "all", `11` = "all", `12` = "all", `13`="all", `14`="all", `15`="all", `16`="all", `17`="all", `18`="all", `19`="all", `20`="all", `21`="all", `22`="all")

marrow.filt.integrated[["pan.ident"]] <-Idents(marrow.filt.integrated)
Idents(marrow.filt.integrated) <-"pan.ident"
levels(Idents(marrow.filt.integrated)) #check it's set to cell cluster names

```

Run bootsrapping for the main clusters
```{r}
marrow_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='all')
#save LKS results
saveRDS(marrow_comp1, "./BootS_ALLres1_KO-vs-WT_unt.rds")
write.csv(marrow_comp1[[1]], "./ALLres1_all-markers.csv")
write.csv(marrow_comp1[[2]]$`100`, "./ALLres1_bootsrap.csv")

marrow_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='all')
saveRDS(marrow_comp2, "./BootS_ALLres2_KO-vs-WT_IL1b.rds")
write.csv(marrow_comp2[[1]], "./ALLres2_all-markers.csv")
write.csv(marrow_comp2[[2]]$`100`, "./ALLres2_bootsrap.csv")

marrow_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='all')
saveRDS(marrow_comp3, "./BootS_ALLres3_IL1b-vs-Veh_WT.rds")
write.csv(marrow_comp3[[1]], "./ALLres3_all-markers.csv")
write.csv(marrow_comp3[[2]]$`100`, "./ALLres3_bootsrap.csv")

marrow_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='all')
saveRDS(marrow_comp4, "./BootS_ALLres4_IL1b-vs-Veh_KO.rds")
write.csv(marrow_comp4[[1]], "./ALLres4_all-markers.csv")
write.csv(marrow_comp4[[2]]$`100`, "./ALLres4_bootsrap.csv")
```

now let's do bootsrapping for individual clusters of interest
```{r}
DefaultAssay(marrow.filt.integrated) <-'RNA'

Idents(marrow.filt.integrated) <- 'seurat_clusters'
#Rename cell clusters as finally agreed upon on Dec 2021
marrow.filt.integrated <- RenameIdents(marrow.filt.integrated, `0` = "CFU-E", `1` = "EryB_CD45-", `2` = "IMP", `3` = "proNeu", `4` = "proNeu", `5` = "IMP", `6` = "HSC", `7` = "MEP", `8` = "Baso", `9` = "preGM", `10` = "Mono", `11` = "Mono", `12` = "MegP", `13`="EryB_CD45+", `14`="Baso", `15`="Neut", `16`="T-cell", `17`="Baso", `18`="Mac", `19`="pDc/B-cell", `20`="CLP", `21`="Eo", `22`="MEP")

marrow.filt.integrated[["cell.ident"]] <-Idents(marrow.filt.integrated)



```


#Run 4 comparison types
  -comp1  Tet2-KO_vs_WT (veh)
  -comp2  Tet2-KO_vs_WT (IL1b)
  -comp3  IL1b_vs_Veh (Tet2-WT)
  -comp4  IL1b_vs_Veh (Tet2-KO)
  
##LKS cells
```{r}



LKS_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='HSC')
LKS_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='HSC')
LKS_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='HSC')
LKS_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='HSC')


#save LKS results
saveRDS(LKS_comp1, "./BootS_LKSres1_KO-vs-WT_unt.rds")
write.csv(LKS_comp1[[1]], "./LKSres1_all-markers.csv")
write.csv(LKS_comp1[[2]]$`100`, "./LKSres1_bootsrap.csv")

saveRDS(LKS_comp2, "./BootS_LKSres2_KO-vs-WT_IL1b.rds")
write.csv(LKS_comp2[[1]], "./LKSres2_all-markers.csv")
write.csv(LKS_comp2[[2]]$`100`, "./LKSres2_bootsrap.csv")

saveRDS(LKS_comp3, "./BootS_LKSres3_IL1b-veh_WT.rds")
write.csv(LKS_comp3[[1]], "./LKSres3_all-markers.csv")
write.csv(LKS_comp3[[2]]$`100`, "./LKSres3_bootsrap.csv")

saveRDS(LKS_comp4, "./BootS_LKSres4_IL1b-veh_KO.rds")
write.csv(LKS_comp4[[1]], "./LKSres4_all-markers.csv")
write.csv(LKS_comp4[[2]]$`100`, "./LKSres4_bootsrap.csv")




```

##IMPs
(formerly CMP & GMP clusters)
```{r}
IMP_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='IMP')
IMP_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='IMP')
IMP_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='IMP')
IMP_comp3[[1]]
IMP_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='IMP')
IMP_comp4[[1]]

saveRDS(IMP_comp1, "./BootS_IMPres1_KO-vs-WT_unt.rds")
write.csv(IMP_comp1[[1]], "./IMPres1_all-markers.csv")
write.csv(IMP_comp1[[2]]$`100`, "./IMPres1_bootsrap.csv")

saveRDS(IMP_comp2, "./BootS_IMPres2_KO-vs-WT_IL1b.rds")
write.csv(IMP_comp2[[1]], "./IMPres2_all-markers.csv")
write.csv(IMP_comp2[[2]]$`100`, "./IMPres2_bootsrap.csv")

saveRDS(IMP_comp3, "./BootS_IMPres3_IL1b-veh_WT.rds")
write.csv(IMP_comp3[[1]], "./IMPres3_all-markers.csv")
write.csv(IMP_comp3[[2]]$`100`, "./IMPres3_bootsrap.csv")


saveRDS(IMP_comp4, "./BootS_IMPres4_IL1b-veh_KO.rds")
write.csv(IMP_comp4[[1]], "./IMPres4_all-markers.csv")
write.csv(IMP_comp4[[2]]$`100`, "./IMPres4_bootsrap.csv")



```

##Monocytes
```{r}



#Monocytes
Mono_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='Mono')
Mono_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='Mono')
Mono_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='Mono')
Mono_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='Mono')


saveRDS(Mono_comp1, "./BootS_Monores1_KO-vs-WT_unt.rds")
write.csv(Mono_comp1[[1]], "./Monores1_all-markers.csv")
write.csv(Mono_comp1[[2]]$`100`, "./Monores1_bootsrap.csv")

saveRDS(Mono_comp2, "./BootS_Monores2_KO-vs-WT_IL1b.rds")
write.csv(Mono_comp2[[1]], "./Monores2_all-markers.csv")
write.csv(Mono_comp2[[2]]$`100`, "./Monores2_bootsrap.csv")

saveRDS(Mono_comp3, "./BootS_Monores3_IL1b-veh_WT.rds")
write.csv(Mono_comp3[[1]], "./Monores3_all-markers.csv")
write.csv(Mono_comp3[[2]]$`100`, "./Monores3_bootsrap.csv")


saveRDS(Mono_comp4, "./BootS_Monores4_IL1b-veh_KO.rds")
write.csv(Mono_comp4[[1]], "./Monores4_all-markers.csv")
write.csv(Mono_comp4[[2]]$`100`, "./Monores4_bootsrap.csv")

```

##proNeu
```{r}


proNeu_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='proNeu')
proNeu_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='proNeu')
proNeu_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='proNeu')
proNeu_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='proNeu')

saveRDS(proNeu_comp1, "./BootS_proNeures1_KO-vs-WT_unt.rds")
write.csv(proNeu_comp1[[1]], "./proNeures1_all-markers.csv")
write.csv(proNeu_comp1[[2]]$`100`, "./proNeures1_bootsrap.csv")

saveRDS(proNeu_comp2, "./BootS_proNeures2_KO-vs-WT_IL1b.rds")
write.csv(proNeu_comp2[[1]], "./proNeures2_all-markers.csv")
write.csv(proNeu_comp2[[2]]$`100`, "./proNeures2_bootsrap.csv")

saveRDS(proNeu_comp3, "./BootS_proNeures3_IL1b-veh_WT.rds")
write.csv(proNeu_comp3[[1]], "./proNeures3_all-markers.csv")
write.csv(proNeu_comp3[[2]]$`100`, "./proNeures3_bootsrap.csv")


saveRDS(proNeu_comp4, "./BootS_proNeures4_IL1b-veh_KO.rds")
write.csv(proNeu_comp4[[1]], "./proNeures4_all-markers.csv")
write.csv(proNeu_comp4[[2]]$`100`, "./proNeures4_bootsrap.csv")
```

##MEPs
```{r}

MEP_comp1 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "KO_unt", cluster='MEP')
MEP_comp2 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_IL1b", ident.2 = "KO_IL1b",cluster='MEP')
MEP_comp3 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "WT_unt", ident.2 = "WT_IL1b",cluster='MEP')
MEP_comp4 <- run.bootstrap(object=marrow.filt.integrated, ident.1 = "KO_unt", ident.2 = "KO_IL1b",cluster='MEP')


saveRDS(MEP_comp1, "./BootS_MEPres1_KO-vs-WT_unt.rds")
write.csv(MEP_comp1[[1]], "./MEPres1_all-markers.csv")
write.csv(MEP_comp1[[2]]$`100`, "./MEPres1_bootsrap.csv")

saveRDS(MEP_comp2, "./BootS_MEPres2_KO-vs-WT_IL1b.rds")
write.csv(MEP_comp2[[1]], "./MEPres2_all-markers.csv")
write.csv(MEP_comp2[[2]]$`100`, "./MEPres2_bootsrap.csv")

saveRDS(MEP_comp3, "./BootS_MEPres3_IL1b-veh_WT.rds")
write.csv(MEP_comp3[[1]], "./MEPres3_all-markers.csv")
write.csv(MEP_comp3[[2]]$`100`, "./MEPres3_bootsrap.csv")

saveRDS(MEP_comp4, "./BootS_MEPres4_IL1b-veh_KO.rds")
write.csv(MEP_comp4[[1]], "./MEPres4_all-markers.csv")
write.csv(MEP_comp4[[2]]$`100`, "./MEPres4_bootsrap.csv")
```


#Find All Markers for GSEA analysis keeping all genes. 
```{r}
#IMP
IMP.cells <- subset(marrow.filt.integrated, idents="IMP")
Idents(IMP.cells) <- "geno_treat"
IMP_all_markers_comp1 <- FindMarkers(IMP.cells,  ident.1 = "WT_unt", ident.2 = "KO_unt", assay = "RNA", logfc.threshold = 0, min.pct = 0)
IMP_all_markers_comp2 <- FindMarkers(IMP.cells,  ident.1 = "WT_IL1b", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
IMP_all_markers_comp3 <- FindMarkers(IMP.cells,  ident.1 = "WT_unt", ident.2 = "WT_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
IMP_all_markers_comp4 <- FindMarkers(IMP.cells,  ident.1 = "KO_unt", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)

IMP_all_markers_comp1[["gene"]] <- rownames(IMP_all_markers_comp1)
IMP_all_markers_comp2[["gene"]] <- rownames(IMP_all_markers_comp2)
IMP_all_markers_comp3[["gene"]] <- rownames(IMP_all_markers_comp3)
IMP_all_markers_comp4[["gene"]] <- rownames(IMP_all_markers_comp4)


write.csv(IMP_all_markers_comp1, "./IMP_all_markers1_GSEA.csv")
write.csv(IMP_all_markers_comp2, "./IMP_all_markers2_GSEA.csv")
write.csv(IMP_all_markers_comp3, "./IMP_all_markers3_GSEA.csv")
write.csv(IMP_all_markers_comp4, "./IMP_all_markers4_GSEA.csv")



#Monocytes
Mono.cells <- subset(marrow.filt.integrated, idents="Mono")
Idents(Mono.cells) <- "geno_treat"
Mono_all_markers_comp1 <- FindMarkers(Mono.cells,  ident.1 = "WT_unt", ident.2 = "KO_unt", assay = "RNA", logfc.threshold = 0, min.pct = 0)
Mono_all_markers_comp2 <- FindMarkers(Mono.cells,  ident.1 = "WT_IL1b", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
Mono_all_markers_comp3 <- FindMarkers(Mono.cells,  ident.1 = "WT_unt", ident.2 = "WT_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
Mono_all_markers_comp4 <- FindMarkers(Mono.cells,  ident.1 = "KO_unt", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)

Mono_all_markers_comp1[["gene"]] <- rownames(Mono_all_markers_comp1)
Mono_all_markers_comp2[["gene"]] <- rownames(Mono_all_markers_comp2)
Mono_all_markers_comp3[["gene"]] <- rownames(Mono_all_markers_comp3)
Mono_all_markers_comp4[["gene"]] <- rownames(Mono_all_markers_comp4)

write.csv(Mono_all_markers_comp1, "./Mono_all_markers1_GSEA.csv")
write.csv(Mono_all_markers_comp2, "./Mono_all_markers2_GSEA.csv")
write.csv(Mono_all_markers_comp3, "./Mono_all_markers3_GSEA.csv")
write.csv(Mono_all_markers_comp4, "./Mono_all_markers4_GSEA.csv")

#proNeu
proNeu.cells <- subset(marrow.filt.integrated, idents="proNeu")
Idents(proNeu.cells) <- "geno_treat"
proNeu_all_markers_comp1 <- FindMarkers(proNeu.cells,  ident.1 = "WT_unt", ident.2 = "KO_unt", assay = "RNA", logfc.threshold = 0, min.pct = 0)
proNeu_all_markers_comp2 <- FindMarkers(proNeu.cells,  ident.1 = "WT_IL1b", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
proNeu_all_markers_comp3 <- FindMarkers(proNeu.cells,  ident.1 = "WT_unt", ident.2 = "WT_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
proNeu_all_markers_comp4 <- FindMarkers(proNeu.cells,  ident.1 = "KO_unt", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)

proNeu_all_markers_comp1[["gene"]] <- rownames(proNeu_all_markers_comp1)
proNeu_all_markers_comp2[["gene"]] <- rownames(proNeu_all_markers_comp2)
proNeu_all_markers_comp3[["gene"]] <- rownames(proNeu_all_markers_comp3)
proNeu_all_markers_comp4[["gene"]] <- rownames(proNeu_all_markers_comp4)

write.csv(proNeu_all_markers_comp1, "./proNeu_all_markers1_GSEA.csv")
write.csv(proNeu_all_markers_comp2, "./proNeu_all_markers2_GSEA.csv")
write.csv(proNeu_all_markers_comp3, "./proNeu_all_markers3_GSEA.csv")
write.csv(proNeu_all_markers_comp4, "./proNeu_all_markers4_GSEA.csv")

#MEP
MEP.cells <- subset(marrow.filt.integrated, idents="MEP")
Idents(MEP.cells) <- "geno_treat"
MEP_all_markers_comp1 <- FindMarkers(MEP.cells,  ident.1 = "WT_unt", ident.2 = "KO_unt", assay = "RNA", logfc.threshold = 0, min.pct = 0)
MEP_all_markers_comp2 <- FindMarkers(MEP.cells,  ident.1 = "WT_IL1b", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
MEP_all_markers_comp3 <- FindMarkers(MEP.cells,  ident.1 = "WT_unt", ident.2 = "WT_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
MEP_all_markers_comp4 <- FindMarkers(MEP.cells,  ident.1 = "KO_unt", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)

MEP_all_markers_comp1[["gene"]] <- rownames(MEP_all_markers_comp1)
MEP_all_markers_comp2[["gene"]] <- rownames(MEP_all_markers_comp2)
MEP_all_markers_comp3[["gene"]] <- rownames(MEP_all_markers_comp3)
MEP_all_markers_comp4[["gene"]] <- rownames(MEP_all_markers_comp4)

write.csv(MEP_all_markers_comp1, "./MEP_all_markers1_GSEA.csv")
write.csv(MEP_all_markers_comp2, "./MEP_all_markers2_GSEA.csv")
write.csv(MEP_all_markers_comp3, "./MEP_all_markers3_GSEA.csv")
write.csv(MEP_all_markers_comp4, "./MEP_all_markers4_GSEA.csv")

#LKS
LKS.cells <- subset(marrow.filt.integrated, idents=c("HSC","preGM"))
Idents(LKS.cells) <- "geno_treat"
LKS_all_markers_comp1 <- FindMarkers(LKS.cells,  ident.1 = "WT_unt", ident.2 = "KO_unt", assay = "RNA", logfc.threshold = 0, min.pct = 0)
LKS_all_markers_comp2 <- FindMarkers(LKS.cells,  ident.1 = "WT_IL1b", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
LKS_all_markers_comp3 <- FindMarkers(LKS.cells,  ident.1 = "WT_unt", ident.2 = "WT_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)
LKS_all_markers_comp4 <- FindMarkers(LKS.cells,  ident.1 = "KO_unt", ident.2 = "KO_IL1b", assay = "RNA", logfc.threshold = 0, min.pct = 0)

LKS_all_markers_comp1[["gene"]] <- rownames(LKS_all_markers_comp1)
LKS_all_markers_comp2[["gene"]] <- rownames(LKS_all_markers_comp2)
LKS_all_markers_comp3[["gene"]] <- rownames(LKS_all_markers_comp3)
LKS_all_markers_comp4[["gene"]] <- rownames(LKS_all_markers_comp4)

write.csv(LKS_all_markers_comp1, "./LKS_all_markers1_GSEA.csv")
write.csv(LKS_all_markers_comp2, "./LKS_all_markers2_GSEA.csv")
write.csv(LKS_all_markers_comp3, "./LKS_all_markers3_GSEA.csv")
write.csv(LKS_all_markers_comp4, "./LKS_all_markers4_GSEA.csv")
```
















